---
title: "Convert Alphanumeric to Decimal"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Convert Alphanumeric to Decimal}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(StringTools)
```

There is currently only a single function in this package, namely, getDecimal. It inputs a string, optionally a base, and outputs a decimal integer. If a base is not specified, then the function will attempt to identify a base. If the string only contains 0s and 1s then binary (base 2) is detected, otherwise if the string contains only numerals 0-9 then decimal (base 10) is detected, otherwise if string only contains 0-f then hex (base 16) is detected, else alphanumeric (base 36) is detected.

Below are some examples of not specifying the base,

```{r}
getDecimal("10")
getDecimal("12")
getDecimal("1f")
getDecimal("1g")
```

And now, below, are examples where we can specify the base,

```{r}
getDecimal("10",3) #base 3
getDecimal("10",11) #base 11
getDecimal("10",27) #base 27
```
